Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-07 tex/paper1/paper1.tex
paper edits and simulated wave

\documentclass[preprint2]{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

%% \documentclass[preprint2]{aastex}

@@

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{Gaussian} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\sigma$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

@@

Section \ref{sec:anal} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a power law-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non-power law power spectrum source over a relatively limited range of
frequencies.  The frequencies at which the Gaussian contribution is
larger than the underlying power-law distribution could be used to
define an average frequency range within which the majority
contribution to the overall Fourier power is not associated with the
underlying power-law distribution.  However, the \Fps\ in this range
would still have to analyzed using both the power-law and Gaussian
contributions to the overall power, and better estimates to the
power-law parameters will be obtained if the full frequency range of
the observations are used.

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for alternating
brightening/darkening in those plots as a indicator of a propagating
wave.  This is essentially a coherence-based approach, as the user is
assessing the likelihood that an oscillation has been detected based
on the observed signal in multiple contiguous pixels.  However, each
pixel in these plots probably has a red-noise background power
spectrum, and so the discussion of Section \ref{ssec:corseis} suggests
that the significance of any claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
the superior description of the observed Fourier power spectrum. The
moss region shows the greatest contribution from the Gaussian
distribution $G(\nu)$ over the background power law.

@@

Comparing the \Fps\ of the simulated observations to the \Fps\ of the
data will bring new constraints on the simulations that will hopefully
improve our understanding of the temporal behavior of the solar
corona.  Further, this paper only considers two of the AIA wave-bands
that are sensitive to higher temperatures.  Using the other
wave-bands, in comparison with the

>>>>

\documentclass{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

%% \documentclass[preprint]{aastex}

@@

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{lognormal} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\sigma$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

@@

Section \ref{sec:anal} demonstrates the presence of a red
noise-like signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a power law-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non-power law power spectrum source over a relatively limited range of
frequencies.  The frequencies at which the lognormal contribution is
larger than the underlying power-law distribution could be used to
define an average frequency range within which the majority
contribution to the overall Fourier power is not associated with the
underlying power-law distribution.  However, the \Fps\ in this range
would still have to analyzed using both the power-law and lognormal
contributions to the overall power, and better estimates to the
power-law parameters will be obtained if the full frequency range of
the observations are used.

@@

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
alternating brightening/darkening in those plots as a indicator of a
propagating wave.  This is essentially a coherence-based approach that
involves an implicit assessment of the likelihood that an oscillation
has been detected.  The basis of the assessment is a judgement that a
signal is seen in multiple contiguous pixels.  However, the results of
Section \ref{sec:anal} suggest that each pixel in these plots has a
red-noise background power spectrum: the discussion of Section
\ref{ssec:corseis} therefore suggests that the significance of any
claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
the superior description of the observed Fourier power spectrum. The
moss region shows the greatest contribution from the lognormal
distribution $G(\nu)$ over the background power law.

@@

Future studies will include examining power spectra at many more
locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
131\AA and 211\AA\ wavebands.  The power-law index in
individual pixels will also be determined, and correlated with other
physical quantiies such as the emission from those pixels.

Finally, a better understanding of the source of the power-law power
spectrum will come from comparing the \Fps\ of simulated observations
to the \Fps\ of the data in all the AIA wave-bands that are sensitive
to higher temperatures.  This will bring new constraints on the
simulations and improve our understanding of the
temporal behavior of the solar corona.
